Prefix-free graphs and suffix array construction in sublinear space

### 2023-06-24 manuscript/main.tex
finished pfg
added abstract

\author[1]{Andrej Baláž}[
    orcid=0000-0001-0002-0003,
    email=andrejbalaz001@gmail.com,
]
\cormark[1]

\author[1]{Alessia Petescia}[
    orcid=0000,
    email=alessia@gmail.com,
]

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Recently, many graph structures for computational pangenomics were proposed.
  In order to be useful, these graph structures need to implement several
  operations such as efficient construction from many complete genomes,
  mapping of short and long read.
  These basic bioinformatics operations are well studied on sequential data,
  and together with data structures such as suffix trees, suffix arrays and 
  burrows wheeler transform allow high performance.
  Attempts to implement these operations on graphs brings with it many complications
  since these date structures are not easily obtainable for graphs.
  In this work, we introduce prefix-free graphs, a pangenomic data structure
  allowing to obtain the well known data structures from stringology in graph
  settings, which in turn allows for many efficient operations on pangenomes.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
  pangenome \sep
  suffix array
\end{keywords}

@@

\input{introduction.tex}

\input{pfg.tex}

\input{sa_construction.tex}

\input{results.tex}

\input{conclusion.tex}

>>>>

\author[1]{Andrej Baláž}[
    email=andrejbalaz001@gmail.com,
]
\cormark[1]

\author[1]{Alessia Petescia}[]

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
    A recent paradigm shift in bioinformatics from a single reference genome to a pangenome brought with it several graph structures.
    These graph structures must implement operations, such as efficient construction from multiple genomes and read mapping.
    Read mapping is a well-studied problem in sequential data, and, together with data structures such as suffix array and Burrows-Wheeler transform, allows for efficient computation.
    Attempts to achieve comparatively high performance on graphs bring many complications since the common data structures on strings are not easily obtainable for graphs.
    In this work, we introduce prefix-free graphs, a pangenomic data structure allowing us to obtain the well-known data structures from stringology in graph settings, allowing for many efficient operations on pangenomes.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
    computational pangenomics \sep
    graph pangenome \sep
    suffix array
\end{keywords}

@@

\input{introduction.tex}
\input{pfg.tex}
\input{sa_construction.tex}
\input{results.tex}
\input{conclusion.tex}
